Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-08-05 manuscript.qmd
add comment on informed consent

Participants were recruited in trains, colleges, universities, adult education centers, fitness studios and various public places in Germany and Austria in November and December 2017. Participation was voluntary and without reimbursement. Each participant was handed a paper and pencil questionnaire, alternating between the 2-point and 6-point response scale versions. When a participant handed back the questionnaire, the facilitator immediately checked for missing values, in which case the participant was politely asked to complete the missing questions. With this procedure, we achieved complete responses for all questionnaires. No power analysis was performed to determine the sample size. Instead, the goal was to collect at least 500 subjects per response format condition over a period of six weeks. No data was analysed before data collection ended.

>>>>

Participants were recruited in trains, colleges, universities, adult education centers, fitness studios and various public places in Germany and Austria in November and December 2017. Participation was voluntary and without reimbursement. Each participant was given a piece of paper informing them about the voluntary and anonymous nature of their participation, the purpose of the study and the data to be collected. When they gave consent, the participant was handed a paper and pencil questionnaire, alternating between the 2-point and 6-point response scale versions. When the participant handed back the questionnaire, the facilitator immediately checked for missing values, in which case the participant was politely asked to complete the missing questions. With this procedure, we achieved complete responses for all questionnaires. No power analysis was performed to determine the sample size. Instead, the goal was to collect at least 500 subjects per response format condition over a period of six weeks. No data was analysed before data collection ended.
